Paper1_V2

### 2022-10-27 scripts/paper1_v3.Rmd
CUP

#input$PAR[which(is.na(input$PAR))] <- (-21.19 + 1.02*(input$SWin)) #not sure that this is right
correction.par<-input$PAR[which(is.na(input$PAR))]
input$PAR[correction.par] <-  replace_na(input$SWin[correction.par] * 4.5 * 0.5) # because NAs at same time can't fill using SWin?

plot(input$Timestamp, input$PAR)

@@

# define seasons (4)
winter <- (input.r$month.name == "Jun" | input.r$month.name == "Jul" |input.r$month.name == "Aug")
spring <- (input.r$month.name == "Sep"| input.r$month.name == "Oct" | input.r$month.name == "Nov")
summer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan" | input.r$month.name == "Feb")
autumn <- (input.r$month.name == "Mar" | input.r$month.name == "Apr" |input.r$month.name == "May")

@@

```{r add lagged variables anf offset variable, echo = FALSE}
input.r$GPP.monthLag <- Lag(input.r$GPP_LT.gC, shift = +30)
input.r$ER.monthLag <- Lag(input.r$ER_LT.gC, shift = +30)
input.r$GPP_offset <- input.r$GPP_LT.gC + 1.25
input.r$ER_ngf.gC <- ifelse(input.r$ER_ngf.gC <0, NA, input.r$ER_ngf.gC)

@@

GPP.summary<- cum.co2fluxes %>% select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(GPP_LT.gC))

@@

plot_grid(TA.GPPL + theme(legend.position = 'none'), TS.GPPL + theme(legend.position = 'none'), 
          P.GPPL + theme(legend.position = 'none'), 
          ET.GPPL+ theme(legend.position = 'none'), SWC.GPPL+ theme(legend.position = 'none'), SWin.GPPL+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)
```

@@

ER.summary<- cum.co2fluxes %>% select(ER_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(ER_LT.gC))

@@

monthlycumsum <- input.r %>%
  select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season, month) %>% 
  group_by(GSYear, month) %>% 
  ddply(c("month", "GSYear"), summarise,
        NEE = sum(NEE_LT.gC),
         GPP = sum(GPP_LT.gC),
         ER = sum(ER_LT.gC),
        GPPneg = -1*sum(GPP_LT.gC))

@@

FFP <- input %>% select(Timestamp, Year, month,L,WS, sigma_v,  WD, ustar, L)
#FFP[2:13] <- as.data.frame(sapply(FFP[2:13], as.numeric)) # convert data frame from character to numeric

@@

FFP <- FFP[, c(1, 2, 3, 9,10,  11, 12, 13, 4, 8, 5,7, 6)] # change variable order to comply with data format

meanmm  <- FFP %>% select(zm, d, L, z0, u_mean, sigma_v, wind_dir, u_star, mm, day, HH_UTC, MM) %>% ddply(c("mm","day", "HH_UTC", "MM"), summarise,
                                                                                                 zm = mean(zm), 
                                                                                                 d = mean(d),
                                                                                                 z0 = mean(z0),
                                                                                                 u_mean = mean(u_mean),
                                                                                                 L = mean(L),
                                                                                                 sigma_v = mean(sigma_v),
                                                                                                 u_star = mean(u_star),
                                                                                                 wind_dir = mean(wind_dir)
                                                                                                 )

@@

>>>>

#input$PAR[which(is.na(input$PAR))] <- (-21.19 + 1.02*(input$SWin)) #not sure that this is right
#correction.par<-input$PAR[which(is.na(input$PAR))]
#input$PAR[correction.par] <-  replace_na(input$SWin[correction.par] * 4.5 * 0.5) # because NAs at same time can't fill using SWin?

#plot(input$Timestamp, input$PAR)

@@

# define seasons (4)
winter <- (input.r$month.name == "Jun" | input.r$month.name == "Jul" |input.r$month.name == "Aug")
spring <- (input.r$month.name == "Sep"| input.r$month.name == "Oct" | input.r$month.name == "Nov")
summer <- (input.r$month.name == "Dec" | input.r$month.name == "Jan" | input.r$month.name == "Feb" | input.r$month.name =="Mar")
autumn <- (input.r$month.name == "Apr" |input.r$month.name == "May")

@@

```{r add lagged variables anf offset variable, echo = FALSE}
#input.r$GPP.monthLag <- Lag(input.r$GPP_LT.gC, shift = +30)
#input.r$ER.monthLag <- Lag(input.r$ER_LT.gC, shift = +30)
input.r$GPP_offset <- input.r$GPP_LT.gC + 1.25
input.r$ER_ngf.gC <- ifelse(input.r$ER_ngf.gC <0, NA, input.r$ER_ngf.gC)

@@

GPP.summary<- cum.co2fluxes %>% dplyr::select(GPP_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(GPP_LT.gC))

@@

#plot_grid(TA.GPPL + theme(legend.position = 'none'), TS.GPPL + theme(legend.position = 'none'), 
 #         P.GPPL + theme(legend.position = 'none'), 
  #        ET.GPPL+ theme(legend.position = 'none'), SWC.GPPL+ theme(legend.position = 'none'), SWin.GPPL+ theme(legend.position = 'none'), GPP.leg.month, ncol = 2)
```

@@

ER.summary<- cum.co2fluxes %>% dplyr::select(ER_LT.gC,dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear, season) %>% 
   ddply(c("GSYear", "season"), summarise,
  seasonal.total = sum(ER_LT.gC))

@@

monthlycumsum <- input.r %>%
  dplyr:: select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season, month) %>% 
  group_by(GSYear, month) %>% 
  ddply(c("month", "GSYear"), summarise,
        NEE = sum(NEE_LT.gC),
         GPP = sum(GPP_LT.gC),
         ER = sum(ER_LT.gC),
        GPPneg = -1*sum(GPP_LT.gC))

@@

FFP <- input %>% dplyr::select(Timestamp, Year, month,L,WS, sigma_v,  WD, u_star)
#FFP[2:13] <- as.data.frame(sapply(FFP[2:13], as.numeric)) # convert data frame from character to numeric

@@

FFP <- FFP[, c(1, 2, 3, 9,10, 6, 11, 12, 13, 4, 8, 5,7)] # change variable order to comply with data format

write.csv(FFP, "C:/Users/Marion/Documents/UTas/FluxProcessing_SilverPlains/FFP.csv")

meanmm  <- FFP %>% dplyr::select(zm, d, L, z0, u_mean, sigma_v, wind_dir, u_star, mm, day, HH_UTC, MM) %>% ddply(c("mm","day", "HH_UTC", "MM"), summarise,
                                                                                                 zm = mean(zm), 
                                                                                                 d = mean(d),
                                                                                                 z0 = mean(z0),
                                                                                                 u_mean = mean(u_mean),
                                                                                                 L = mean(L),
                                                                                                 sigma_v = mean(sigma_v),
                                                                                                 u_star = mean(u_star),
                                                                                                 wind_dir = mean(wind_dir)
                                                                                                 )

@@

```{r Carbon uptake period}
summer.input <- input.r %>% filter (season == "Summer" | season =="Autumn")

cum.co2fluxes.sum <- summer.input%>%
  dplyr::select(NEE_LT.gC, GPP_LT.gC, ER_LT.gC, dayssinceJun1, GSYear, season) %>% 
  group_by(GSYear) %>% 
  mutate(NEEcum = cumsum(NEE_LT.gC),
         GPPcum = cumsum(GPP_LT.gC),
         ERcum = cumsum(ER_LT.gC))

(NEEcum.p <-cum.co2fluxes.sum %>% 
  ggplot(., aes(dayssinceJun1, NEEcum, group = GSYear, color = GSYear)) +
  geom_line(size = 1, aes(color = GSYear))+
   # scale_color_manual(values = group.colour)+
       scale_x_continuous(limits = c(184, 365))+
  ylab(bquote('Cumulative NEE (g C ' ~m^-2~')'))+
  xlab("Days since June 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

(NEEtime.p <-summer.input%>%
  ggplot(., aes(dayssinceJun1, NEE_LT.gC, color = GSYear)) +
  geom_line()+
        #scale_color_manual(values = group.colour)+
       scale_x_continuous(limits = c(184, 365))+

  ylab(bquote(' NEE (g C ' ~m^-2~')'))+
  xlab("Days since June 1st")+
  theme_classic()+ 
    theme(axis.title = element_text(size = 14),
          axis.text = element_text(size = 13)))

CO2uptakesum <- summer.input %>% filter(NEE_LT.gC<0)
CO2uptakesum.1920 <- CO2uptakesum %>% filter(GSYear == '19/20') #49
CO2uptakesum.2021 <- CO2uptakesum %>% filter(GSYear == '20/21') #101
CO2uptakesum.2122 <- CO2uptakesum %>% filter(GSYear == '21/22') #107
